---
title: "Leading indicators of market growth"
author: "John M. Drake"
date: "2025-07-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache=TRUE)
```

## Background

Here we analyze a time series of data provided by Marcus Cunha for Thoughtful Insights. 
The objective is to illustrate a use case for statistical leading indicators based on the theory of critical slowing down.

## Data

First we read in the data.

```{r data}
data <- read.csv('kpi-data.csv')
```

Calculate total revenue as $REVENUE = MRR + NMRR + Expansion$.

```{r}
data$revenue <- data$MRR + data$NMRR + data$Expansion
```

Plot two variables (`revenue` and `Clients`) on ordinary and logarthmic scales.

```{r plot}
par(mfrow=c(2,2))
plot(data$Clients, type='l', xlab='Time', ylab='Clients', main='Ordinary scale')
plot(data$Clients, type='l', log='y', xlab='Time', ylab='Clients', main='Logarithmic scale')
plot(data$revenue, type='l', xlab='Time', ylab='Revenue', main='Ordinary scale')
plot(data$revenue, type='l', log='y', xlab='Time', ylab='Revenue', main='Logarithmic scale')
```